Figure Extra

### 2022-07-15 Figures/Figure2.Rmd
new deconvolution result location

```{r}
read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/julien/gemdecan/data/all_deconvolutions/all_deconvolutions_all_TCGA.txt") %>%
  mutate_at("Samples", str_remove_all, ".01A*") %>%
  mutate_at("Samples", str_replace_all, "-", ".") %>% 
  group_by(Samples) %>%
  summarise_all(mean) -> tcga_deconv

>>>>

```{r}
read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/data/deconvolution_for_gemdecan/all_deconvolutions_all_TCGA.txt") %>%
  mutate_at("Samples", str_remove_all, ".01A*") %>%
  mutate_at("Samples", str_replace_all, "-", ".") %>% 
  group_by(Samples) %>%
  summarise_all(mean) -> tcga_deconv

### 2022-07-15 Figures/Figures_nonTCGA.Rmd
new deconvolution result location

# GSE72056
## Data loading
```{r}
deconv_GSE72056 <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #! fix naming of deconv results

@@

# Thomas RNAseq #! Change name!
## Data loading
```{r}
deconv_Thomas <- read_tsv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Private/Miguel/Projects/CRCT/21 - Epigenomics and network modelling of heterogeneity in immuno-oncology/Ting Xie/2021/CIBERSORTx/final_example_signatures/all_deconvolutions/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
  dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
  dplyr::rename_with(~str_replace(.,"__", "_"))#! fix naming of deconv results

>>>>

# GSE72056
## Data loading
```{r}
deconv_GSE72056 <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Melanoma_GSE72056_no_malighant.txt") %>% dplyr::rename_with(~str_replace(.,"__", "_CBSX_"))  %>% dplyr::rename_with(~str_replace(.,"__", "_")) #! fix naming of deconv results

@@

# Thomas RNAseq #! Change name!
## Data loading
```{r}
deconv_Thomas <- read_csv("/mnt/SERVER-CRCT-STORAGE/CRCT21/Data/deconvolution_for_gemdecan/all_deconvolutions_Thomas_RNAseq_part.txt") %>%
  dplyr::rename_with(~str_replace(.,"__", "_CBSX_")) %>%
  dplyr::rename_with(~str_replace(.,"__", "_"))#! fix naming of deconv results
